A Switching Planner for Combined Task and Observation Planning

### 2010-11-20 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
I think, sequential, rather than serial, is a better term.

\include{macros}

@@

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Switching in Continual Planning for Practical Robot Control}
\title{A Switching Planner for Combined Task and Observation Planning}
%\title{A Continual Planner that Switches Between Serial and
%  Decision-Theoretic Planning} 
\author{NA}
\setcounter{secnumdepth}{0}

@@

the speed and scalability of software for serial planning in
deterministic

@@

We have extended MAPSIM to simulate DTPDDL instances, and modified
\fastdownward\ so that it can find useful serial executions given
DTPDDL models of the problem at hand.

 called DTPDDL, along
the lines of PDDL for the partially observable case, an \laostar\
solution procedure, a determinisation of the DTPDDL problem in MAPL,
and modify the \fastdownward\ system to find high quality serial plans
.

@@

\section{Serial Planning in Determinisations}

@@

There have been a number of developments recently towards planning
under uncertainty using systems that were intended for serial planning
in deterministic problems.  Notably,
\system{FFR$_a$}~\cite{yoon:etal:2007}, the winning entry from the
probabilistic track of the 2004 International Planning Competition,
uses the fast satisficing procedure
\system{FF}~\cite{hoffmann:nebel:2001} to compute a serial plan and
corresponding execution trace. The resulting plan is then executed
until the observed trace deviates from the planned trace.

@@

More computationally expensive approaches in this vein combine
sampling strategies on valuations over {\em runtime variables} with
deterministic planning procedures. The outcome is typically a more
robust serial plan~\cite{yoon:etal:2008}, or contingent
plan~\cite{majercik:2006}.

%%
Recently the systems
\system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009}, demonstrated how conformant
planning ---i.e., serial planning in unobservable worlds--- can be
modelled as a deterministic problem, and therefore solved using serial
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. This
research thread has also been extended recently to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.

@@

In this paper we address these challenges, developing a continual
planner that switches between sequential and decision-theoretic
planning. Given a POMDP model of the environment, serial planning is
responsible for an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until an assumption about a runtime proposition

@@

Interaction between the serial planner and execution proceeds
more-or-less analogously to popular replanning approaches

Addressing these challenges in a monolithic framework, we present a
{\em switching} continual planner, that uses the fast serial
satisficing procedure FastDownward to perform net-benefit
%%
makes reasonable assumptions about the evolution of the runtime state
given a POMDP model of the environment.

@@

computing a single serial plan and
eventuality

>>>>

\include{macros}%

@@

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Switching in Continual Planning for Practical Robot Control}
\title{A Switching Planner for Combined Task and Observation Planning}
%\title{A Continual Planner that Switches Between Sequential and
%  Decision-Theoretic Planning} 
\author{NA}
\setcounter{secnumdepth}{0}

@@

the speed and scalability of software for sequential planning in
deterministic

@@

We have extended MAPSIM to parse and simulate DTPDDL problems, and
modified \fastdownward\ so that it can find useful sequential executions
given DTPDDL models of the problem at hand.

 called DTPDDL, along
the lines of PDDL for the partially observable case, an \laostar\
solution procedure, a determinisation of the DTPDDL problem in MAPL,
and modify the \fastdownward\ system to find high quality sequential plans
.

@@

\section{Sequential Planning in Determinisations}

@@

There have been a number of developments recently towards planning
under uncertainty using systems that were intended for sequential planning
in deterministic problems.  Notably,
\system{FFR$_a$}~\cite{yoon:etal:2007}, the winning entry from the
probabilistic track of the 2004 International Planning Competition,
uses the fast satisficing procedure
\system{FF}~\cite{hoffmann:nebel:2001} to compute a sequential plan and
corresponding execution trace. The resulting plan is then executed
until the observed trace deviates from the planned trace.

@@

More computationally expensive approaches in this vein combine
sampling strategies on valuations over {\em runtime variables} with
deterministic planning procedures. The outcome is typically a more
robust sequential plan~\cite{yoon:etal:2008}, or contingent
plan~\cite{majercik:2006}.

%%
Recently the systems
\system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009}, demonstrated how conformant
planning ---i.e., sequential planning in unobservable worlds--- can be
modelled as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. This
research thread has also been extended recently to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.

@@

In this paper we address these challenges, developing a continual
planner that switches between sequential and decision-theoretic
planning. Given a POMDP model of the environment, sequential planning is
responsible for an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until an assumption about a runtime proposition

@@

Interaction between the sequential planner and execution proceeds
more-or-less analogously to popular replanning approaches

Addressing these challenges in a monolithic framework, we present a
{\em switching} continual planner, that uses the fast sequential
satisficing procedure FastDownward to perform net-benefit
%%
makes reasonable assumptions about the evolution of the runtime state
given a POMDP model of the environment.

@@

computing a single sequential plan and
eventuality
